Machine Learning and Constraint Programming for Relational-To-Ontology Schema Mapping

### 2017-09-04 stp/paper_aaai/main.tex
Typo
Fixed colors and couple fo typos

We formulate the problem of semantic labeling as a multi-class classification
problem.
The known source descriptions $S_T$ provide us the training sample.
We compute a feature vector for each attribute in a data source and associate 
the known semantic type with the corresponding feature vector.
The feature vector, among others, includes characteristics
such as a number 
of whitespaces and other special characters, statistics of 
values in the column 
%(e.g, mean/max/min string length and numeric statistics)
, etc. 
A full list can be found in Appendix \ref{Ann:SemLab}.
%\npr{If I remove entropy descr, we are perfectly within page limit}
%\ignore{
One of the important features characterising information content of an attribute is Shannon's entropy.
% of the attribute's concatenated rows
Shannon's entropy 
%(or information entropy~\cite{Manning:Introduction})
 of a string $X$ is defined as
$H(X) = -\sum_{i}{p_i \log_{2}p_i},$ where $p_i$ is the probability of a character, whose index in character vocabulary is $i$, to appear in $X$, and the summation ranges over all
characters in the vocabulary.
%of all possible characters
To evaluate $p_i$ in Shannon's entropy, we evaluate normalized character frequency distribution \emph{chardist} of an attribute, as character counts in concatenated rows of the attribute, normalized by the total length of the concatenated rows.
The vocabulary of all characters consists of 100 printable characters (including $\backslash$n).
Finally, we add the 100-dimensional vector of $p_i$ to the attribute feature vector.
%}
We also compute a set of features based on similarity metrics inspired by state-of-the-art works~\cite{Pham:semantic} or~\cite{Ritze:matching}.
Among others, we compute mean cosine similarity for character distributions of attribute values and string similarity metrics for attribute names.
%To extract features from attribute names, we compute string similarity metrics: minimum edit distance, two WordNet based similarity measures such as JCN~\cite{Jiang:Semantic} and LIN ~\cite{Lin:Information}, and $k$-nearest neighbors using Needle-Wunsch distance~\cite{Needleman:General}.
%The minimum edit distance between two strings $s_1$ and $s_2$ is the minimum number of edit operations, such as insertion, deletion, substitution, which are required to transform one string into another~\cite{Manning:Introduction}.
%We compute the similarity between attribute name and all class instances in the training data.
%The number of thus extracted features depends on the number of semantic labels in the training data.
We train a random forest on the obtained sample.

@@

		\end{axis}
	\end{tikzpicture}
\subcaption{Recall (soccer)}\label{fig:soccerrec}
\end{minipage}%
\caption{Performance for the museum and soccer domains. 
Average size of integration graphs for the museum domain: 88 nodes and 1129 edges2.
Average run time for the museum domain: \serene{} 0.5s, \karma{} 0.5s, \serenepats{} 1s. \label{fig:perf}}
\vspace{-3mm}
\end{figure}

@@

%%%%%%% Steiner Tree Problem
int: nbV;                               % Nb of nodes in alignment graph
int: nbE;                               % Nb of edges in alignment graph
set of int: nodes = 1..nbV;    
set of int: edges = 1..nbE;
set of int: cnodes;                     % Class nodes in alignment graph
set of int: dnodes;                     % Data nodes in alignment graph
set of int: anodes;                     % Attribute nodes in alignment graph (normally none)
array [nodes] of var bool: vs;          % Is a node of the alignment graph in the solution?
array [edges] of var bool: es;          % Is an edge of the alignment graph in the solution?
array [nodes,edges] of bool: adjacent;  % adjacent[n,e] <=> node n is an endnode of edge e
array [edges] of nodes: heads;          % endpoint 1 of each edge (The graph is undirected!!)
array [edges] of nodes: tails;          % endpoint 2 of each edge
array[1..2,edges] of int: endpairs = array2d(1..2,edges,tails++heads);
array [edges] of int: ws;               % Weights of edges in alignment graph
var 0..sum(ws): w;                      % Weight of the solution corresponding to the alignment part
constraint steiner_tree(vs,es,adjacent,endpairs,w,ws);  % Steiner Tree constraint
constraint forall (d in dnodes) (vs[d] <-> sum(e in edges where adjacent[d,e])(es[e]) == 1); %Only 1 edges per data node

%%%%%%% Matching Problem
int: nbA;                                           % Nb of attribute nodes
set of int: atts = 1..nbA;                 
array [atts] of set of int: attribute_domains;      % Data nodes to which each attribute can attach  
constraint forall(att in anodes) (vs[att] == true); % Attribute nodes (normally none) are in the graph.
array [atts] of var int: match;                     % Match between Attributes and Data nodes
array[atts,int] of int: match_costs;                % Weight of match edges
constraint forall (a in atts) (match[a] in (attribute_domains[a]));   % Must match someone in the domain
constraint forall (a in atts) (vs[match[a]]);       % The data node matched must be in the subgraph of the alignment
constraint alldifferent(match);                     % Exact match
var 0..sum(a in atts)(sum(n in index_set_2of2(match_costs))(match_costs[a,n])): wm;  %Total cost from matching part :
constraint wm = sum(a in atts) (match_costs[a,match[a]]);

@@

%%%%%%% Patterns
int: nb_patterns;                     %Number of patterns
set of int: PATTS = 1..nb_patterns;
array[PATTS] of int: patterns_w;      %Support of patterns
array[PATTS] of set of int: patterns; %The actual patterns
array[PATTS] of var bool: c_p;        %Is pattern chosen
constraint forall (p in PATTS) ((sum (e in patterns[p])   % All edges of a pattern are used <-> pattern is used
							                  	(es[e]) == card(patterns[p])) <-> c_p[p]);
var 0..sum(patterns_w): wp; % Total prize collected from patterns : 
constraint if nb_patterns = 0 then wp = 0 else wp = sum(p in PATTS) (c_p[p] * patterns_w[p]) endif;

>>>>

We formulate the problem of semantic labeling as a multi-class classification
problem.
The known source descriptions $S_T$ provide us the training sample.
We compute a feature vector for each attribute in a data source and associate 
the known semantic type with the corresponding feature vector.
The feature vector, among others, includes characteristics
such as a number 
of whitespaces and other special characters, statistics of 
values in the column 
%(e.g, mean/max/min string length and numeric statistics)
, etc. 
A full list can be found in Appendix \ref{Ann:SemLab}.
%\npr{If I remove entropy descr, we are perfectly within page limit}
%\ignore{
One of the important features characterising information content of an attribute is Shannon's entropy.
% of the attribute's concatenated rows
Shannon's entropy 
%(or information entropy~\cite{Manning:Introduction})
 of a string $X$ is defined as
$H(X) = -\sum_{i}{p_i \log_{2}p_i},$ where $p_i$ is the probability of a character, whose index in character vocabulary is $i$, to appear in $X$, and the summation ranges over all
characters in the vocabulary.
%of all possible characters
To evaluate $p_i$ in Shannon's entropy, we evaluate normalized character frequency distribution \emph{chardist} of an attribute, as character counts in concatenated rows of the attribute, normalized by the total length of the concatenated rows.
The vocabulary of all characters consists of 100 printable characters (including $\backslash$n).
Finally, we add the 100-dimensional vector of $p_i$ to the attribute feature vector.
%}
We also compute a set of features based on similarity metrics inspired by state-of-the-art works by ~\citeasnoun{Pham:semantic} or~\citeasnoun{Ritze:matching}.
Among others, we compute mean cosine similarity for character distributions of attribute values and string similarity metrics for attribute names.
%To extract features from attribute names, we compute string similarity metrics: minimum edit distance, two WordNet based similarity measures such as JCN~\cite{Jiang:Semantic} and LIN ~\cite{Lin:Information}, and $k$-nearest neighbors using Needle-Wunsch distance~\cite{Needleman:General}.
%The minimum edit distance between two strings $s_1$ and $s_2$ is the minimum number of edit operations, such as insertion, deletion, substitution, which are required to transform one string into another~\cite{Manning:Introduction}.
%We compute the similarity between attribute name and all class instances in the training data.
%The number of thus extracted features depends on the number of semantic labels in the training data.
We train a random forest on the obtained sample.

@@

		\end{axis}
	\end{tikzpicture}
\subcaption{Recall (soccer)}\label{fig:soccerrec}
\end{minipage}%
\caption{Performance for the museum and soccer domains. 
Average size of integration graphs for the museum domain: 88 nodes and 1129 
edges.
Average run time for the museum domain: \serene{} 0.5s, \karma{} 0.5s, \serenepats{} 1s. \label{fig:perf}}
\vspace{-3mm}
\end{figure}

@@

%%%%%%% Steiner Tree Problem
int: nbV;                               % Nb of nodes in alignment graph
int: nbE;                               % Nb of edges in alignment graph
set of int: nodes = 1..nbV;    
set of int: edges = 1..nbE;
set of int: cnodes;                     % Class nodes in alignment graph
set of int: dnodes;                     % Data nodes in alignment graph
set of int: anodes;                     % Attribute nodes in alignment graph (normally none)
array [nodes] of var bool: vs;          % Is a node of the alignment graph in the solution?
array [edges] of var bool: es;          % Is an edge of the alignment graph in the solution?
array [nodes,edges] of bool: adjacent;  % adjacent[n,e] <=> node n is an endnode of edge e
array [edges] of nodes: heads;          % endpoint 1 of each edge (The graph is undirected!!)
array [edges] of nodes: tails;          % endpoint 2 of each edge
array[1..2,edges] of int: endpairs = array2d(1..2,edges,tails++heads);
array [edges] of int: ws;               % Weights of edges in alignment graph
var 0..sum(ws): w;                      % Weight of the solution corresponding to the alignment part
constraint steiner_tree(vs,es,adjacent,endpairs,w,ws);  % Steiner Tree constraint
constraint forall (d in dnodes) 
                   (vs[d] <-> sum(e in edges where adjacent[d,e])(es[e]) == 1);% Only 1 edges per data node

%%%%%%% Matching Problem
int: nbA;                                           % Nb of attribute nodes
set of int: atts = 1..nbA;                 
array [atts] of set of int: attribute_domains;      % Data nodes to which each attribute can attach  
constraint forall(att in anodes) (vs[att] == true); % Attribute nodes (normally none) are in the graph.
array [atts] of var int: match;                     % Match between Attributes and Data nodes
array[atts,int] of int: match_costs;                % Weight of match edges
constraint forall (a in atts) (match[a] in (attribute_domains[a]));   % Must match someone in the domain
constraint forall (a in atts) (vs[match[a]]);       % The data node matched must be in the subgraph of the alignment
constraint alldifferent(match);                     % Exact match
var 0..sum(a in atts)(sum(n in index_set_2of2(match_costs))(match_costs[a,n])): wm;  % Total cost from matching part :
constraint wm = sum(a in atts) (match_costs[a,match[a]]);

@@

%%%%%%% Patterns
int: nb_patterns;                     % Number of patterns
set of int: PATTS = 1..nb_patterns;
array[PATTS] of int: patterns_w;      % Support of patterns
array[PATTS] of set of int: patterns; % The actual patterns
array[PATTS] of var bool: c_p;        % Is pattern chosen
constraint forall (p in PATTS) ((sum (e in patterns[p])   % All edges of a pattern are used <-> pattern is used
							                  	(es[e]) == card(patterns[p])) <-> c_p[p]);
var 0..sum(patterns_w): wp;           % Total prize collected from patterns : 
constraint if nb_patterns = 0 then wp = 0 else wp = sum(p in PATTS) (c_p[p] * patterns_w[p]) endif;
